IGRINS spectra of \name

### 2016-05-04 document/ms.tex
Framework for answering the question: At what phase of variability were the spectra acquired? Issue #18

>>>>

Figure XX shows the data of XX plotted from the interval X-Y.  Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.  The ESPaDoNs spectra were at a phase of Z, indicating...

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/V_phot_phase.pdf}
	\caption{Estimated $V$-band photometry phase during the times of observations.}
	\label{fig:PhotPhase}
\end{figure*}
